---
title       : 2010 Census - Web based reactive graphical interface
subtitle    : cousera project - June 2014
author      : Ami
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Source of Data 

### 2010 Census data

Looking at the census data is a hard task:
```{r}
data<-readRDS("./data/counties.rds")

data[1:5,1:6]
```

--- .class #id 

## Data Exploration

Even looking at the summary stats is not easy:

```{r}
summary(data)
```

---

## The Interactive Graphical Web App

Instead, I have created a web-interface to graphically explore the data and get graphs like:

```{r fig.width=7, fig.height=6}
white<-data$white
hist(white)
```

---

## Now it is simple and easy to explore the data


### Easy to launch:

###### library(shiny)
###### runGitHub ("project", username="amimiz")


